Weather

### 2021-10-08 Weather.Rmd
nkj

```{r}
library(tidyverse) # Data wrangling
library(lubridate) # Dates operations
library(daymetr)
library(chirps)
library(patchwork)
library(ggtext)
library(ggthemes)
library(nasapower)
library(ggdist)
library(vegan)
```

>>>>

```{r}
library(tidyverse) # Data wrangling
library(lubridate) # Dates operations
library(daymetr)
library(chirps)
library(patchwork)
library(ggtext)
library(ggthemes)
library(nasapower)
library(ggdist)
library(vegan)
#https://cran.r-project.org/web/packages/ggdist/vignettes/slabinterval.html
```
